Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-28 Ben_Manuscripts/structure_paper/Draft.tex
Revisions, citations and new figures

  The broadening of the $q_z$ cross-section of R-$\pi$ is related to
  $z$-directional correlation between scatters within monomer columns. The
  correlation length varies as the inverse of the full width at half maximum
  (FWHM) of the $q_z$ cross-section of R-$\pi$.  Using this technique, we
  calculated the correlation length of the experimental system to be 9.0 \AA. As
  scatterers become less correlated, we expect that R-$\pi$ will broaden.

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental % reference needed
  resolution.  In our simulated XRD patterns, the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.

@@

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.pdf}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  %MRS15: 95% is fine.
  \includegraphics[width=\textwidth]{offset_ecdfs.pdf}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration are symmetric, implying that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

>>>>

  The broadening of the $q_z$ cross-section of R-$\pi$ is related to
  $z$-directional correlation between scatters within monomer columns. The
  correlation length varies as the inverse of the full width at half maximum
  (FWHM) of the $q_z$ cross-section of R-$\pi$~\cite{young_highly_2013-1}. Using
  this technique, we calculated the correlation length of the experimental 
  system to be 9.0 \AA. As scatterers become less correlated, we expect that
  R-$\pi$ will broaden.

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental % reference needed
  resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
  the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.pdf}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  %MRS15: 95% is fine.
  \includegraphics[width=\textwidth]{offset_ecdfs.pdf}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration are symmetric, implying that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

### 2018-09-28 Ben_Manuscripts/structure_paper/supporting_information.tex
Revisions, citations and new figures

@@

>>>>

  \newpage

@@

  \section{Ensemble of ordered sandwiched configurations}

  Here we show the results of the same analysis shown in Figures~\ref{M-fig:ensemble_XRD} 
  and~\ref{M-fig:full_ensemble_distributions} of the main text for the 
  ordered sandwiched ensemble of configurations.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.pdf}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ecdfs.pdf}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration are symmetric, implying that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.pdf}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_means.pdf}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered sandwiched system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}
